Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
Small fix
fixed ILP terminology

We consider various sets of cells in tables:
\begin{itemize}
  \item {\bf Cells}: Each entry in the matrix/table is called  a \textit{cell}.
  We use the notation $T[a,b]$ to refer to a particular cell in the table~$T$ at the row with index~$a$ and the column with index~$b$.
  \item {\bf Columns and rows}: To refer to the $a$-th row (column) we use the following syntax $T[a,{:}]$ ($T[{:},a]$), to refer to a subrange from $a$ to $b$ we use $T[a{:}b,]$ ($T[,a{:}b]$).
  \item
  A \textit{vector} is either a column or a row that is type-consistent.
  If a vector is a row (column), we say that it has a \textit{row} (\textit{column}) orientation.
  \item
  A \textit{group} is a subrange of vectors with the same orientation in a table.
  We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers.
  We denote as the \textit{length} of a row (column) group $G$, written as \textit{length(G)}, the number of its columns (rows). We call a group $G$ \textit{numeric} (\textit{textual}, etc), written as \textit{numeric(G)}, if all its vectors contain numeric (textual, etc) elements.
  \item
 A \textit{subgroup} $g$ is a subrange of vectors belonging to a group $G$. If the subgroup $g$ must contain only one vector, we write $g \in G$.
%We refer to a subgroup of a group $G$ in \groups as $g$. A \textit{subgroup} $g$ is a subrange of vectors in a group $G$. If a subgroup $g$ must contain only one vector, we write $g \in G$.
% A \textit{subgroup} $G'$ is a subrange of vectors belonging to a group $G$. If the subgroup $\{v\}$ must contain only one vector, we write $v \in G$.
\end{itemize}
For notational convenience, we will refer to vectors with $V$ and to groups and subgroups with $G$.

@@

\subsection{Constraints}
\sergey{write correspondence with ILP terminology}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on each of them. 
\begin{itemize}
\item
\textit{\CName} is the textual name of the constraint together with the list of its variables $v_1,\dots,v_n$.  In ILP terminology, it is known as vocabulary.
\item
  \textit{\CSignature} is a set of constraints on the properties of the group assignments, corresponding to the variables $v_1,\dots,v_n$ in \CName.
  For example, the signature can restrict the types of the groups, e.g., requiring them to be integers or constrain their sizes, e.g. the length of vectors in the arguments must be equal.
  The constraints act on properties or group meta-information, not on the actual group content. In ILP, it is known as mode declarations, when one needs to declare types of variables in the vocabulary. Also, it is analogous to standard linear algebra well-defined requirements, e.g., in order to multiply matrices $A$ and $B$, $A$ must have the size of $n \times k$ and $B$ the size $k \times m$.
\item \textit{\CFunction} is a constraint specifying that the data in the subgroups satisfies the function. In ILP, it is known as bias, where we constrain ourselves to only particular subset of language in which we perform the search. 
\end{itemize}

@@

\paragraph{Example}
The \ecrank{v_y}{v_x} constraint requires $v_y$ to consist of only integer or only textual data and $v_x$ to be numeric.
This allows to filter candidate groups for these variables.
Additionally, $v_y$ and~$v_x$ must be vectors of the same length, therefore, only groups with the same length are considered.
Groups that do not satisfy these requirements cannot contain subgroups (vectors) that satisfy \ecrank{v_y}{v_x}.

>>>>

We consider various sets of cells in tables:
\begin{itemize}
  \item {\bf Cells}: Each entry in the matrix/table is called  a \textit{cell}.
  We use the notation $T[a,b]$ to refer to a particular cell in the table~$T$ at the row with index~$a$ and the column with index~$b$.
  \item {\bf Columns and rows}: To refer to the $a$-th row (column) we use the following syntax $T[a,{:}]$ ($T[{:},a]$), to refer to a subrange from $a$ to $b$ we use $T[a{:}b,]$ ($T[,a{:}b]$).
  \item
  A \textit{vector} is either a column or a row that is type-consistent.
  If a vector is a row (column), we say that it has a \textit{row} (\textit{column}) orientation.
  \item
  A \textit{group} is a subrange of vectors with the same orientation in a table.
  We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers.
  We denote as the \textit{length} of a row (column) group $G$, written as \textit{length(G)}, the number of its columns (rows). We call a group $G$ \textit{numeric} (\textit{textual}, etc), written as \textit{numeric(G)}, if all its vectors contain numeric (textual, etc) elements.
  \item
 A \textit{subgroup} $g$ is a subrange of vectors belonging to a group $G$. If the subgroup $g$ must contain only one vector, we write $g \in G$.it defines what it means for a constraint be well-formed
%We refer to a subgroup of a group $G$ in \groups as $g$. A \textit{subgroup} $g$ is a subrange of vectors in a group $G$. If a subgroup $g$ must contain only one vector, we write $g \in G$.
% A \textit{subgroup} $G'$ is a subrange of vectors belonging to a group $G$. If the subgroup $\{v\}$ must contain only one vector, we write $v \in G$.
\end{itemize}
For notational convenience, we will refer to vectors with $V$ and to groups and subgroups with $G$.

@@

\subsection{Constraints}
\sergey{write correspondence with ILP terminology}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on each of them. 
\begin{itemize}
\item
\textit{\CName} is the textual name of the constraint together with the list of its variables $v_1,\dots,v_n$.  In ILP terminology, it is known as vocabulary.
\item
  \textit{\CSignature} is a set of constraints on the properties of the group assignments, corresponding to the variables $v_1,\dots,v_n$ in \CName.
  For example, the signature can restrict the types of the groups, e.g., requiring them to be integers or constrain their sizes, e.g. the length of vectors in the arguments must be equal.
  The constraints act on properties or group meta-information, not on the actual group content. In ILP, it is known as bias, it defines what it means for a constraint be well-formed.
  \item \textit{\CFunction} is a constraint specifying that the data in the subgroups satisfies the function. In ILP, it is known as background knowledge, which provides a definition to a predicate.
\end{itemize}

@@

\paragraph{Example}
The \ecrank{v_y}{v_x} constraint requires $v_y$ to consist of only integer or only textual data and $v_x$ to be numeric.
This allows us to filter candidate groups for these variables.
Additionally, $v_y$ and~$v_x$ must be vectors of the same length, therefore, only groups with the same length are considered.
Groups that do not satisfy these requirements cannot contain subgroups (vectors) that satisfy \ecrank{v_y}{v_x}.
